The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-02-27 paper.tex
about to start chopping apart the results and discussion section

 \hline
Survey & $\left< z \right> $ & $\left< log\left(\frac{M_{\star}}{M_{\odot}}\right)\right>$ & $\left< \frac{V_{C}}{\sigma_{int}} \right>$ & med$\left(\frac{V_{C}}{\sigma_{int}}\right)$ & RDF & $ \left< \sigma_{int} \right>$ & med$\left(\sigma_{int}\right)$ & $\left<V_{C}\right>$ & med$\left(V_{C}\right)$  \\
 \hline
 GHASP & 0.001 & 10.6 & $12.91^{+0.51}_{-0.44}$ & $12.45^{+5.15}_{-5.05}$ & $1.0^{+0.00}_{-0.024}$ & $13.0^{+0.5}_{-0.5}$ & $13.0^{+6.0}_{-4.0}$ & $189.0^{+3.5}_{-3.0}$ & $159.4^{+113.3}_{-79.2}$ \\
 DYNAMO & 0.1 & 10.3 & $5.06^{+0.18}_{-0.15}$ & $4.55^{+3.06}_{-2.22}$ & $0.96^{+0.02}_{-0.015}$ & $45.9^{+0.3}_{-0.3}$ & $39.0^{+18.2}_{-21.9}$ & $183.0^{+1.0}_{-1.0}$ & $164.0^{+76.0}_{-50.0}$ \\
 KROSS & 0.9 & 9.9 & $3.05^{+0.17}_{-0.17}$ & $2.36^{+2.64}_{-1.46}$ & $0.81^{+0.05}_{-0.05}$ & - & - & $117.0^{+4.0}_{-4.0}$ & $109^{+77.0}_{-66.0}$ \\
 KMOS$^{3D}$ & 1.0 & 10.7 & 5.5 & - & 0.93 & 25 & - & 170 & - \\
 MASSIV & 1.2 & 10.2 & $2.41^{+1.4}_{-0.9}$ & $1.95^{+2.40}_{-1.31}$ & $0.67^{+0.06}_{-0.06}$ & $61.8^{+3.8}_{-4.2}$ & $52.0^{+23.2}_{-20.7}$ & $132.13^{+10.4}_{-8.2}$ & $103.0^{+99.0}_{-61.2}$ \\
 SINS(C09) & 2.0 & 10.6 & $5.0^{+0.93}_{-0.97}$ & $4.74^{+1.11}_{-0.18}$ & 1.0 & $51.2^{+8.0}_{-7.9}$ & $42.5^{+14.5}_{-3.5}$ & $232.0^{+12.8}_{-12.7}$ & $240.0^{+31.0}_{-60.2}$ \\
 SINS(F09) & 2.0 & 10.6 & 2.6 & - & 0.60 & - & - & $201.3^{+4.3}_{-4.0}$ & $174.0^{+83.0}_{-58.0}$ \\
 KMOS$^{3D}$ & 2.2 & 10.9 & 2.6 & - & 0.73 & 55 & - & 170 & - \\
 AMAZE & 3.0 & 10.0 & $3.59^{+1.45}_{-1.1}$ & $2.1^{+4.7}_{-1.15}$ & 0.33 & $85.9^{+1.5}_{-1.4}$ & $78.0^{+27.0}_{-48.0}$ & $217^{+59.1}_{-40.2}$ & $129^{+166.0}_{-50.2}$ \\
 KDS & 3.5 & 10.0 & $1.125^{+0.18}_{-0.15}$ & $0.99^{+0.59}_{-0.34}$ & $0.37^{+0.08}_{-0.08}$ & $70.8^{+3.3}_{-3.1}$ & $67.0^{+18.4}_{-19.0}$ & $78.8^{+5.4}_{-5.1}$ & $60.0^{+49.1}_{-18.2}$ \\
 \hline
\end{tabular}
  \end{threeparttable}
  \end{table*}

@@

\subsection{GHASP}\label{subsec:GHASP}
The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ in the local universe ($z\sim0$) to derive 3D H$\alpha$ datacubes.
The data extend out to several half-light radii and in each case an analytic function is fit to determine $V_{C}$, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
We use the tabulated values from this survey as a local comparison sample.

\subsection{DYNAMO}\label{subsec:DYNAMO}
In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}[M_{\odot}])=10.3$ at $z\sim0.1$ is presented.
The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, making this an excellent sample for comparisons to high redshift.
$V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.3R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{subsec:redshift_evolution} to highlight the difference in selection critera.

\subsection{KROSS}\label{subsec:KROSS}
We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\sim600$ SFGs with median $log(M_{\star}[M_{\odot}])=9.9$ and $z\sim0.9$.
$V_{C}$ values are extracted from exponential disk fits to the data at $2R_{1/2}$ (differing from arctangent fits by a median of 0.5\%) with the $\sigma_{int}$ values also extracted at $2R_{1/2}$ when the data extend to this radius and when they do not $\sigma_{int}$ is taken to be the median of the $\sigma_{obs}$ map.
These quantities are then beam-smearing corrected as described in H17 section 3.3.3. 
Due to the consistency of modelling and measurement techniques these form a robust $z\sim0.9$ comparison sample.

\subsection{KMOS$^{3D}$}\label{subsec:kmos_3d}
The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
At $z \sim 1.0$ the galaxies have $log(M_{\star}[M_{\odot}])=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}[M_{\odot}])=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}[M_{\odot}])=10.0$.   The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{subsec:redshift_evolution} plots.

\subsection{MASSIV}\label{subsec:MASSIV}
The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}[M_{\odot}])=10.2$ at $z\sim1.2$.
An arctangent function is fit to the data and $V_{C}$ is extracted at $\sim1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
We make use of tabulated values presented in E12.

\subsection{SINS}\label{subsec:SINS}
The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ at $z\sim2.0$.
Galaxies in this sample are classified as rotation or dispersion dominated following FS09 section 9.5.1 which classifies rotation dominated galaxies using the observed velocity and integrated velocity dispersion criteria $V_{obs}/(2\sigma_{tot}) > 0.4$.
$V_{C}$ values for rotation dominated galaxies are computed using a combined velocity gradient + width approach \citep{ForsterSchreiber2006} and for dispersion dominated galaxies using the velocity width.
Only integrated velocity dispersions are presented for the full sample.
In addition, \cite[C09]{Cresci2009} model robust rotators in the SINS sample using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
In this approach the $V_{C}$ value comes from the best fitting model parameter and $\sigma_{int}$ is calculated using equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.

@@

\subsection{LAW 09}\label{subsec:law_09}
In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}[M_{\odot}])=10.0$ at $z\sim2.3$.
The `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ without inclination correction and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
We note that the $\sigma_{mean}$ values and errors tabulated in \cite{Law2009} paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have beam beam-smearing corrected, or extracted at the galaxy outskirts where the effects of beam-smearing are much smaller.
We use tabulated data $\sigma_{int}$ data in L09 to compare this distribution with other results, but make no comparisons with the observed velocity-shear values.

\subsection{AMAZE}\label{subsec:AMAZE}
The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}[M_{\odot}])=9.9$ at z $\sim 3$, closest in redshift to the KDS galaxies.
In this study rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam-smearing (see their Eq. 8).
A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotationally dominated galaxies in their sample, with the remaining 22 galaxies not analysed.
We use tabulated values from G11, however we note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion dominated galaxies. \\

>>>>

 \hline
Survey & $\left< z \right> $ & $\left< log\left(\frac{M_{\star}}{M_{\odot}}\right)\right>$ & $\left< \frac{V_{C}}{\sigma_{int}} \right>$ & med$\left(\frac{V_{C}}{\sigma_{int}}\right)$ & RDF & $ \left< \sigma_{int} \right>$ & med$\left(\sigma_{int}\right)$ & $\left<V_{C}\right>$ & med$\left(V_{C}\right)$  \\
 \hline
 GHASP & 0.001 & 10.6 & $12.91^{+0.51}_{-0.44}$ & $12.45^{+5.15}_{-5.05}$ & $1.0^{+0.00}_{-0.024}$ & $13.0^{+0.5}_{-0.5}$ & $13.0^{+6.0}_{-4.0}$ & $189.0^{+3.5}_{-3.0}$ & $159.4^{+113.3}_{-79.2}$ \\
 DYNAMO & 0.1 & 10.3 & $5.06^{+0.18}_{-0.15}$ & $4.55^{+3.06}_{-2.22}$ & $0.96^{+0.02}_{-0.015}$ & $45.9^{+0.3}_{-0.3}$ & $39.0^{+18.2}_{-21.9}$ & $183.0^{+1.0}_{-1.0}$ & $164.0^{+76.0}_{-50.0}$ \\
 KROSS & 0.9 & 9.9 & $3.05^{+0.17}_{-0.17}$ & $2.36^{+2.64}_{-1.46}$ & $0.81^{+0.05}_{-0.05}$ & - & - & $117.0^{+4.0}_{-4.0}$ & $109^{+77.0}_{-66.0}$ \\
 KMOS$^{3D}$ & 1.0 & 10.7 & 5.5 & - & 0.93 & 25 & - & 170 & - \\
 MASSIV & 1.2 & 10.2 & $2.41^{+1.4}_{-0.9}$ & $1.95^{+2.40}_{-1.31}$ & $0.67^{+0.06}_{-0.06}$ & $61.8^{+3.8}_{-4.2}$ & $52.0^{+23.2}_{-20.7}$ & $132.13^{+10.4}_{-8.2}$ & $103.0^{+99.0}_{-61.2}$ \\
 SINS(C09) & 2.0 & 10.6 & $5.0^{+0.93}_{-0.97}$ & $4.74^{+1.11}_{-0.18}$ & 1.0 & $51.2^{+8.0}_{-7.9}$ & $42.5^{+14.5}_{-3.5}$ & $232.0^{+12.8}_{-12.7}$ & $240.0^{+31.0}_{-60.2}$ \\
 SINS(F09) & 2.0 & 10.6 & 2.6 & - & 0.60 & - & - & $201.3^{+4.3}_{-4.0}$ & $174.0^{+83.0}_{-58.0}$ \\
 KMOS$^{3D}$ & 2.2 & 10.9 & 2.6 & - & 0.73 & 55 & - & 170 & - \\
 AMAZE & 3.0 & 10.0 & $3.59^{+1.45}_{-1.1}$ & $2.1^{+4.7}_{-1.15}$ & 0.33 & $85.9^{+1.5}_{-1.4}$ & $78.0^{+27.0}_{-48.0}$ & $217^{+59.1}_{-40.2}$ & $129^{+166.0}_{-50.2}$ \\
 \textbf{KDS} & 3.5 & 10.0 & $1.125^{+0.18}_{-0.15}$ & $0.99^{+0.59}_{-0.34}$ & $0.37^{+0.08}_{-0.08}$ & $70.8^{+3.3}_{-3.1}$ & $67.0^{+18.4}_{-19.0}$ & $78.8^{+5.4}_{-5.1}$ & $60.0^{+49.1}_{-18.2}$ \\
 \hline
\end{tabular}
  \end{threeparttable}
  \end{table*}

@@

\subsection{GHASP ($z\sim0$)}\label{subsec:GHASP}
The GHASP survey \citep[E08]{Epinat2008,Epinat2008a} makes use of Fabry-Perot observations of 203 spiral and irregular galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ in the local universe ($z\sim0$) to produce 3D H$\alpha$ datacubes.
The data extend out to several half-light radii and in each case tilted ring models are fit to determine $V_{C}$ at large radii where the rotation curves have flattened, with $\sigma_{int}$ given as the dispersion in the rotation velocity across the whole field.
We use the tabulated values from this survey as a local comparison sample.

\subsection{DYNAMO ($z\sim0.1$, but selected with physical properties resembling $z\sim2$)}\label{subsec:DYNAMO}
In the DYNAMO survey \citep[G14]{Green2014}, H$\alpha$ IFU data of 67 galaxies with median $log(M_{\star}[M_{\odot}])=10.3$ at $z\sim0.1$ is presented.
The selection criteria is such that half of the sample have high sSFR representative of SFGs at $z\sim 2$, and are also found to have higher $f_{gas}$ values than locally, mimicking the physical conditions of $z\sim 2$ SFGs.
$V_{C}$ values are extracted at a fixed radius from an arctangent model fit to the velocity fields ($1.6R_{1/2}$ as measured in the r-band) and $\sigma_{int}$ is taken as the luminosity weighted average of the beam-smearing corrected dispersion field.
We make use of tabulated data from this survey, but use clear symbols throughout the plots in \cref{subsec:redshift_evolution} to highlight the difference in selection critera.

\subsection{KROSS ($z\sim0.9$)}\label{subsec:KROSS}
We make comparisons to the most recent KROSS results \citep[H17]{Harrison2017}, which presents KMOS H$\alpha$ observations of $\sim600$ SFGs with median $log(M_{\star}[M_{\odot}])=9.9$ and $z\sim0.9$.
$V_{C}$ values are extracted from exponential disk fits to the data at $2R_{1/2}$ (differing from arctangent fits by a median of 0.5\%) with the $\sigma_{int}$ values also extracted at $2R_{1/2}$ when the data extend to this radius and when they do not $\sigma_{int}$ is taken to be the median of the $\sigma_{obs}$ map.
These quantities are then beam-smearing corrected as described in H17 section 3.3.3. 
Due to the consistency of modelling and measurement techniques these form a robust $z\sim0.9$ comparison sample.

\subsection{KMOS$^{3D}$ ($z\sim1.0$ and $z\sim2.3$)}\label{subsec:kmos_3d}
The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
At $z \sim 1.0$ the galaxies have $log(M_{\star}[M_{\odot}])=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}[M_{\odot}])=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}[M_{\odot}])=10.0$.   The rotation velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{subsec:redshift_evolution} plots.

\subsection{MASSIV ($z\sim1.2$)}\label{subsec:MASSIV}
The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}[M_{\odot}])=10.2$ at $z\sim1.2$.
An arctangent function is fit to the data and $V_{C}$ is extracted at $\sim1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
We make use of tabulated values presented in E12.

\subsection{SINS ($z\sim2.0$)}\label{subsec:SINS}
The SINS survey \citep[FS09]{ForsterSchreiber2009} presents SINFONI $H\alpha$ observations of 80 massive galaxies with median $log(M_{\star}[M_{\odot}])=10.6$ at $z\sim2.0$.
Galaxies in this sample are classified as rotation or dispersion dominated following FS09 section 9.5.1 which classifies rotation dominated galaxies using the observed velocity and integrated velocity dispersion criteria $V_{obs}/(2\sigma_{tot}) > 0.4$.
$V_{C}$ values for rotation dominated galaxies are computed using a combined velocity gradient + width approach \citep{ForsterSchreiber2006} and for dispersion dominated galaxies using the velocity width.
Only integrated velocity dispersions are presented for the full sample.
In addition, \cite[C09]{Cresci2009} model robust rotators in the SINS sample using the IDL code DYSMAL, which derives rotation curves given an input radial mass distribution.
In this approach the $V_{C}$ value comes from the best fitting model parameter and $\sigma_{int}$ is calculated using equation \ref{eq:sins_sigma}, with the best fitting $\sigma_{01}$ used (reflecting thin and thick disks; see their text for more detail) and with $\sigma_{02}$, an additional component of isotropic velocity dispersion throughout the disk, left as a free parameter in the fitting.

@@

\subsection{LAW 09 ($z\sim2.3$)}\label{subsec:law_09}
In \cite[L09]{Law2009} OSIRIS [O~{\sc III}]$\lambda$5007 and H$\alpha$ observations are collected for 13 galaxies with median $log(M_{\star}[M_{\odot}])=10.0$ at $z\sim2.3$.
The `velocity shear' is computed as $v_{shear} = \frac{1}{2}(v_{max} - v_{min})$ without inclination correction and $\sigma_{int}$ is the flux-weighted mean of $\sigma_{obs}$.
We note that the $\sigma_{mean}$ values and errors tabulated in \cite{Law2009} paper are the flux weighted mean and standard deviation of the measurements in individual spaxels in each galaxy, not corrected for beam-smearing in any way.
These measurements are expected to be larger than the $\sigma_{int}$ measurements at similar redshift which have beam beam-smearing corrected, or extracted at the galaxy outskirts where the effects of beam-smearing are much smaller.
We use tabulated data $\sigma_{int}$ data in L09 to compare this distribution with other results, but make no comparisons with the observed velocity-shear values.

\subsection{AMAZE ($z\sim3.0$)}\label{subsec:AMAZE}
The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}[M_{\odot}])=9.9$ at z $\sim 3$, closest in redshift to the KDS galaxies.
In this study rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam-smearing (see their Eq. 8).
A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotationally dominated galaxies in their sample, with the remaining 22 galaxies not analysed.
We use tabulated values from G11, however we note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion dominated galaxies. \\
